%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[12pt, a4paper]{awesome-cv}

\def\sidemargin{2.4cm}
\def\topbotmargin{2.4cm}
\geometry{top=\topbotmargin, bottom=\topbotmargin, left=\sidemargin, right=\sidemargin}
\fontdir[fonts/] % Specify the location of the included fonts

\usepackage{pagecolor}
\definecolor{page}{HTML}{fefdfa}
\pagecolor{page}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
% \colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
\definecolor{awesome}{HTML}{559CC7}

% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{333B42}
\definecolor{text}{HTML}{080808}
\definecolor{graytext}{HTML}{555E66}
\definecolor{lighttext}{HTML}{8B9297}


% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\renewcommand{\acvHeaderAfterNameSkip}{2.8mm}
\renewcommand{\acvHeaderAfterPositionSkip}{0.8mm}
\renewcommand{\acvHeaderAfterAddressSkip}{0.1mm}
\renewcommand{\acvSectionTopSkip}{2mm}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./img/profile}
\name{Werner}{Bisschoff}
\position{Software Engineer}
\address{Cape Town, Western Cape, South Africa}

\email{werner@bisschoff.dev}
% \mobile{067 081 7719}
\whatsapp{071 826 2066}
\homepage{werner.bisschoff.dev} %TODO: add website
% \github{wbisschoff13}
\linkedin{wbisschoff13}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
% \recipient
%   {Company Recruitment Team}
%   {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
% \lettertitle{Job Application}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Best Regards,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% \makecvfooter
% {\today}
% {Claud D. Park~~~·~~~Cover Letter}
% {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  \lettersection{About Me}

  I am a software engineer with over 5 years of experience bridging hardware, full-stack development, and resilient system architecture. My approach combines deep technical expertise with a \textbf{rigorous, AI-augmented methodology}—utilizing agentic workflows to ship reliable software at high velocity. With a background in Computer and Electronic Engineering (B.Eng.), I don't just write code; I design \textbf{systems that last}, from low-level firmware to cloud-native infrastructures.

  \lettersection{Why Me?}

  \textbf{Hard Engineering \& System Design:} My foundations are in complex, real-time systems. At Ingenics Digital, I designed an event-driven finite state machine for embedded systems using \textbf{C++ and FreeRTOS}, creating a maintainable architecture that reduced bugs and accelerated development cycles. Whether I am working with memory-constrained microcontrollers or distributed cloud services, I prioritize long-term maintainability and architectural integrity.

  \textbf{Strategic AI Integration:} I treat AI as a powerful force multiplier for my existing engineering skills, applying it where it offers the greatest leverage while remaining fully capable of developing complex systems manually. I use \textbf{Claude Code} for surgical, interactive debugging and \textbf{Droid by Factory} for programmatic automation. This allows me to maintain high code quality and rigour while moving at the pace of a modern, high-impact environment, without incurring technical debt.

  \textbf{Full-Stack Versatility \& Impact:} My technical breadth is grounded in practical delivery. At FARO Africa, I extended ERPNext systems (Python/JS), built mobile features in Expo with NFC integration, and provisioned AWS infrastructure with Pulumi. This versatility is complemented by my \textbf{"impact over process"} philosophy—demonstrated by my work founding \textit{Divergent Tabletop}, where I apply systems thinking to solve real-world community challenges.

  \textbf{Resilient Infrastructure:} Beyond application code, I am comfortable with the "plumbing" of modern software, including \textbf{Docker} for development and CI/CD. I am currently preparing to open-source my community wiki project, reflecting my commitment to shared knowledge and the Open Source ecosystem.

  I would welcome the opportunity to discuss how my blend of engineering rigour and AI leverage can help your team maximize its impact.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
